Variable Selection in Convex Function Estimation

### 2013-10-01 tex/scam/appendix.tex

 We will use covering number and uniform convergence and will thus need to first introduce some notations.

@@

@@

Define $f^{*s} = \arg\min \{ R_s(f) \,|\, f \in \mathcal{C}^s[b,B,L], \E f_k(X_k) = 0\}$.

Define $f^{*(s-1)} = \arg\min \{ R_s(f) \,|\, f \in \mathcal{C}^{(s-1)}[b,B,L], \E f_k(X_k) = 0\}$, the optimal solution with only $s-1$ components.

By Theorem~\ref{thm:convex_faithful}, $R_s(f^*_s) - R_s(f^*_{(s-1)}) \geq \alpha > 0$.

@@

$f_0 - f^{*s}$ is bounded by $2sB$ and $w_i$ is zero-mean subgaussian with scale $\sigma$. Therefore, $\|w\|_n$ is at most $c\sigma$ with probability at least $1-\frac{C}{n}$ for all $n > n_0$.

So we derive that, with probability at least $1 -\frac{C}{n}$, for all $n > n_0$,
\[
|\hat{R}_s(f^{*s} - \bar{f}^{*s}) - \hat{R}_s(f^{*s})|\leq 2csB(B+\sigma) \sqrt{\frac{1}{cn} \log sn}
\]

>>>>

 We will use covering number and uniform convergence and will thus need to first introduce some notations. 
 \subsubsection{Notation}

@@

Define $f^{*s} = \arg\min \{ R_s(f) \,|\, f \in \mathcal{C}^s[b,B,L], \, \E f_k(X_k) = 0\}$.

Define $f^{*(s-1)} = \arg\min \{ R_s(f) \,|\, f \in \mathcal{C}^{(s-1)}[b,B,L], \, \E f_k(X_k) = 0\}$, the optimal solution with only $s-1$ components.

\subsubsection{Proof}

\begin{lemma}

\end{lemma}

By Theorem~\ref{thm:convex_faithful}, $R_s(f^{*s}) - R_s(f^{*(s-1)}) \geq \alpha > 0$.

@@

@@

$\|f_0 - f^{*s}\|_n \leq \|f_0 - f^{*s}\|_\infty $ is bounded by $2sB$ and $w_i$ is zero-mean subgaussian with scale $\sigma$. Therefore, $\|w\|_n$ is at most $c\sigma$ with probability at least $1-\frac{C}{n}$ for all $n > n_0$.

So we derive that, with probability at least $1 -\frac{C}{n}$, for all $n > n_0$,
\[
|\hat{R}_s(f^{*s} - \bar{f}^{*s}) - \hat{R}_s(f^{*s})| \leq 2csB(B+\sigma) \sqrt{\frac{1}{cn} \log sn}
\]
